Creating More Meaningful Explanations for Audio Deepfake Detection

### 2025-01-24 draft.tex
add to results section

		A summary of some experiments based on the method described above is provided below. The
		model that achieved the best results was trained and evaluated using the methods
		previously described, has an evaluation accuracy of 96.3\% with the default threshold of

@@

>>>>

		A summary of some experiments based on the method described above is provided in table
		\ref{table:eval-results}. The model that achieved the best results was trained on the
		first 10000 samples of the dataset and evaluated on the rest evaluated using the methods
		previously described. It has an evaluation accuracy of 96.3\% with the default threshold of

@@

		\begin{table}[htbp]
			\begin{tabular}{c | c | c | c}
				Terminus & Training & Accuracy & EER \\
				\hline
				Simple & until 3474 & 95.02\% & 0.03702 \\
				3 hidden layers & until 10000 & 96.27\% & 0.03214 \\
				Simple & until 23833 2 epochs & 90.07\% & 0.90069 \\
				Simple & until 10000 2 epochs & 94.43\% & 0.04408 \\
				Simple & until 10000 & 94.28\% & 0.04840
			\label{table:eval-results}
			\caption{Summary of the evaluation results of the experiments}
		\end{table}
